A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-10 text/survival.Rmd
Add Figure 4 forest heatmap with figure legend. Update text to reflect figure 4. Adjust manuscript.rmd to work with docx
merge with upstream, and make progress on doing a large multi-component survival figure

![](../figures/fig6B.png)
![](../figures/fig6C.png)
<p style="FONT-SIZE:10px; COLOR:#000000; LINE-HEIGHT:12px;">**Figure 5: relative survival of pathway clusters. a) Posterior distributions of estimated relative age-dependent survival by cancer type. b) Posterior distributions of estimated class-dependent survival for each cancer type. See methods for model details.</p>

@@

```{r survival-model, eval=FALSE}

![**Figure 6B**](../figures/fig6B.png)

![**Figure 6C**](../figures/fig6C.png)

>>>>

```{r survfig}

library(ggridges)
library(patchwork)

load("../code/survival/survmodel-ethbkd.stansave")

cancerdat = read_csv("../data/survival/clinical_plus_cluster.csv");
cancerdat$type = as.factor(cancerdat$type)

dfsamps = as.data.frame(sampseth)

kcancplot = function(dfsamps,tisnames){
	ktisnames = grep("ktis",names(dfsamps),value=TRUE)
	dfktis = dfsamps[,ktisnames]
	dfktis = stack(dfktis) ## convert to two column "values" and "ind" with "ind" being the name of the variable
	names(dfktis) = c("value","parname")

	dim(tisnames) = c(length(tisnames),1)

	dfktis$cancname = sapply(dfktis$parname,function(x) tisnames[x])
	ggplot(dfktis) + geom_density_ridges(aes_(~value,~cancname))+ theme_minimal() + scale_fill_brewer(palette="Paired") + xlim(0,22) + labs(x="ktis multiplier",y="Cancer Type",title="Tissue Specific Effects")
}

kclassplot = function(dfsamps,tisnames){
	kclnames = grep("k\\[",names(dfsamps), value=TRUE)
	dfclas = dfsamps[,kclnames]
	dfclas = stack(dfclas)
	names(dfclas) = c("value","coefname")
	dfclas$class = as.numeric(gsub("k\\[(.*),(.*)\\]","\\2",dfclas$coefname))
	dfclas$tiss = tisnames[as.numeric(gsub("k\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
	ggplot(dfclas) + geom_density_ridges(aes_(~value,~class)) +
		facet_wrap(. ~ tiss,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
		xlim(0,3) + theme(legend.position = "none") + ggtitle("Class Specific Coefficients")
}

p1 = kcancplot(dfsamps,levels(cancerdat$type))
p2 = kclassplot(dfsamps,levels(cancerdat$type))

p1 + p2

@@
